### 2019-01-21 writing/thesis/chapters/conclusion.tex
Final (?) changes.

\chapter{Conclusion}\label{chap:conclusion}
We implemented a \muscl{}-limited \aderdg{}-scheme with \amr{} for the reactive Navier Stokes equations in this thesis.
We showed that the scheme works and is capable of simulation different scenarios:
\begin{itemize}
\item We showed in \cref{sec:results-convergence} that our scheme converges for all considered orders for the Navier-Stokes equations.
\item We evaluated our method for standard \textsc{cfd} scenarios~(\cref{sec:cfd}) and achieved competitive results for all used scenarios.
  This is true for both two-dimensional scenarios (Taylor-Green and Lid-Driven Cavity) and for the three-dimensional \textsc{abc}-flow.
\item Furthermore, our method allows us to simulate flows in hydrostatic equilibrium correctly (see \cref{sec:results-cloud}).
\item The results of \cref{sec:results-tts-amr} showed that our \amr{}-criterion is able to save a significant portion of the computational effort compared to a uniform fine grid.
  It is able to do this without degrading the quality of the solution, even for a scenario that contains small-scale details.
\item Our results of \cref{sec:results-reactive} show that our implementation is capable of simulating chemical reactions with a limited scheme, at least for a source term that is not stiff.
\end{itemize}

Of course, there are some things that can be improved and which need further work, such as:
\begin{itemize}
\item The current treatment of the boundary conditions is not stable for some scenarios.
  Especially the viscous walls for the \muscl{}-method are not correct, due to limitations of \exahype{}.
\item The \textsc{cfl}-condition~\pcref{eq:cfl-aderdg,eq:cfl-muscl} has the effect that our method needs a large number of timesteps.
  Even though our \amr{}-criterion is able to reduce the number of needed cells drastically, we could get another large improvement by utilizing local time-stepping.
\item Our implementation of the \textsc{cj}-detonation wave cannot handle realistic detonations because we do not have an implementation of stiff source terms.
  An implementation of this is straight-forward but includes changes to the space-time predictor and its initial guess, and also to the \muscl{}-scheme.
\end{itemize}

>>>>

\chapter{Conclusion}\label{chap:conclusion}
We implemented a \muscl{}-limited \aderdg{}-scheme with \amr{} for the reactive Navier Stokes equations in this thesis.
We showed that the scheme works and is capable of simulation different scenarios:
\begin{itemize}
\item We showed in \cref{sec:results-convergence} that our scheme converges for all considered orders for the Navier-Stokes equations.
\item We evaluated our method for standard \textsc{cfd} scenarios~(\cref{sec:cfd}) and achieved competitive results for all used scenarios.
  This is true for both two-dimensional scenarios (Taylor-Green vortex and lid-driven cavity) and for the three-dimensional \textsc{abc}-flow.
\item Furthermore, our method allows us to simulate flows in hydrostatic equilibrium correctly (see \cref{sec:results-cloud}).
\item The results of \cref{sec:results-tts-amr} showed that our \amr{}-criterion is able to save a significant portion of the computational effort compared to a uniform fine grid.
  It is able to do this without degrading the quality of the solution, even for a scenario that contains small-scale details.
\item Our results of \cref{sec:results-reactive} showed that our implementation is capable of simulating chemical reactions with a limited scheme, at least for a source term that is not stiff.
\end{itemize}

Of course, there are some things that can be improved and which need further work, such as:
\begin{itemize}
\item The current treatment of the boundary conditions is not stable for some scenarios.
  Especially the viscous walls for the \muscl{}-method are not correct, due to limitations of \exahype{}.
\item The \textsc{cfl}-condition~\pcref{eq:cfl-aderdg,eq:cfl-muscl} has the effect that our method needs a large number of timesteps.
  Even though our \amr{}-criterion is able to reduce the number of needed cells drastically, we could get another large improvement by utilizing local time-stepping.
\item Our implementation of the \textsc{cj} detonation wave cannot handle realistic detonations because we do not have an implementation of stiff source terms.
  An implementation of this is straight-forward but includes changes to the space-time predictor and its initial guess, and also to the \muscl{}-scheme.
\end{itemize}

### 2019-01-21 writing/thesis/chapters/implementation.tex
Final (?) changes.

\section{Implementing numerics}
We needed to modify the existing implementation of the mappings, solvers and kernels to be able to solve problems with diffusive fluxes.
These changes are:
\begin{itemize}
\item Modifying the space-time-predictor (defined in file \fileName{spaceTimePredictorNonlinear.cpph}).
  \begin{itemize}
  \item The function \funName{aderPicardLoopNonlinear} implements the space-time-predictor loop \pcref{eq:space-time-predictor}.
    We pass the gradient of the conserved variables to the \funName{flux} method of the \className{Solver}.
    Because we need the time-average of the gradient later, we return it.
   \item In the function \funName{aderExtrapolatorNonlinear}, which implements the boundary extrapolation, we also compute the extrapolated gradient.
    \item In the function \funName{spaceTimePredictorNonlinear}, we also return the extrapolated gradient.
  \end{itemize}
\item Storing the extrapolated and time-averaged gradient for each cell for use in the boundary conditions and the corrector step.
\item Using the gradient for the computation of the boundary conditions.
  They are defined in the file \fileName{boundaryConditions.cpph}.
\item Adding the diffusive penalty terms for the Riemann solver\\(\fileName{riemannSolverNonlinear.cpph}) and \textsc{cfl}-condition (\fileName{stableTimeStepSize.cpph}).
  This corresponds to \cref{eq:rusanov-flux,eq:cfl-aderdg}.
\item Computing the gradient for the \muscl{} scheme (\fileName{musclhancock.cpph}) and passing it to the flux (\fileName{rusanov.cpph}).
\end{itemize}
Additionally, we needed to change the templates for the glue code and needed to modify some function signatures to accompany the other changes.

>>>>

\section{Implementing Numerics}
We needed to modify the existing implementation of the mappings, solvers and kernels to be able to solve problems with diffusive fluxes.
These changes are:
\begin{itemize}
\item Modifying the space-time-predictor (defined in file \fileName{spaceTimePredictorNonlinear.cpph}).
  \begin{itemize}
  \item The function \funName{aderPicardLoopNonlinear} implements the space-time-predictor loop \pcref{eq:space-time-predictor}.
    We pass the gradient of the conserved variables to the \funName{flux} method of the \className{Solver}.
    Because we need the time-average of the gradient later, we return it.
   \item In the function \funName{aderExtrapolatorNonlinear}, which implements the boundary extrapolation, we also compute the extrapolated gradient.
    \item In the function \funName{spaceTimePredictorNonlinear}, we also return the extrapolated gradient.
  \end{itemize}
\item Storing the extrapolated and time-averaged gradient for each cell for use in the boundary conditions and the corrector step.
\item Using the gradient for the computation of the boundary conditions.
  They are defined in the file \fileName{boundaryConditions.cpph}.
\item Adding the diffusive penalty terms for the Riemann solver\\(\fileName{riemannSolverNonlinear.cpph}) and \textsc{cfl}-condition (\fileName{stableTimeStepSize.cpph}).
  This corresponds to \cref{eq:rusanov-flux,eq:cfl-aderdg}.
\item Computing the gradient for the \muscl{} scheme (\fileName{musclhancock.cpph}) and passing it to the flux (\fileName{rusanov.cpph}).
\end{itemize}
Additionally, we needed to change the templates for the glue code and needed to modify some function signatures to accompany the other changes.

### 2019-01-21 writing/thesis/chapters/introduction.tex
Final (?) changes.

Of course, a finer grid is not useful if the computational effort is too large.
Thus, also propose a compute rate of one simulated years per wall-clock day.
An example of a recent supercomputing effort in this domain~\cite{fuhrer2018near} achieved a performance of 0.043 simulated years per wall-clock day with a resolution of $\SI{930}{\m}$ for a near-global simulation on the Piz Daint supercomputer.
They used the \textsc{cosmo} 5.0 model which is based on a finite-difference approach.

\sidetitle{Discontinuous Galerkin}
The discontinuous Galerkin (\dg{}) methods are an exciting numerical method as they are relatively easy to scale.
In addition, they can be of high order and can perform local grid refinement~\cite{hesthaven2008nodal}.
These advantages are only some reasons why they have been investigated for weather and climate modeling~\cite{muller2010adaptive,giraldo2008study}.
Recently, \ader{} discontinuous Galerkin methods has been proposed, for example in~\cite{dumbser2008unified}.
This method is scalable and of arbitrary order in both time and space.
With an appropriate limiter, it is also stable, even in the vicinity of discontinuities~\cite{dumbser2016simple}.
It is thus a promising candidate for a numerical scheme for the exascale era.

The goal of this thesis is to evaluate the \aderdg{} method for testing scenarios, which have been devised as benchmark examples for meteorological applications~\cite{robert1993bubble,giraldo2008study}.
We implement this with the \exahype{}-engine, which is \enquote{An Exascale Hyperbolic \pde{} Engine}.

>>>>

Of course, a finer grid is not useful if the computational effort is too large.
Thus they propose a compute rate of one simulated years per wall-clock day.
An example of a recent supercomputing effort in this domain~\cite{fuhrer2018near} achieved a performance of 0.043 simulated years per wall-clock day with a resolution of $\SI{930}{\m}$ for a near-global simulation on the Piz Daint supercomputer.
They used the \textsc{cosmo} 5.0 model which is based on a finite-difference approach.

\sidetitle{Discontinuous Galerkin}
The discontinuous Galerkin (\dg{}) methods are exciting numerical schemes as they are relatively easy to scale.
In addition, they can be of high order and can perform local grid refinement~\cite{hesthaven2008nodal}.
These advantages are only some reasons why they have been investigated for weather and climate modeling~\cite{muller2010adaptive,giraldo2008study}.
Recently, \ader{} discontinuous Galerkin methods has been proposed, for example in~\cite{dumbser2008unified}.
These methods are scalable and of arbitrary order in both time and space.
With an appropriate limiter, they are also stable, even in the vicinity of discontinuities~\cite{dumbser2016simple}.
They are thus promising numerical methods, even for the exascale era.

The goal of this thesis is to evaluate the \aderdg{} method of~\cite{dumbser2008unified} for testing scenarios, which have been devised as benchmark examples for meteorological applications~\cite{robert1993bubble,giraldo2008study}.
We implement this with the \exahype{}-engine, which is \enquote{An Exascale Hyperbolic \pde{} Engine}.
